### 2019-08-21 thesis.tex
almost there

In terms of the normalized variables and quantities, the equations
for $L$ and $S$ waves, including the contributions from non-eigenmode
fluctuations, become
\begin{equation}
  \begin{split}
    \frac{\partial\calE_{\bf q}^{\sigma L}}{\partial\tau}
  &=\mu_{\bf q}^L\,\frac{\pi}{q^2}\int d{\bf u}\;
    \delta(\sigma z_{\bf q}^L-{\bf q}\cdot{\bf u})\\
    &\times\biggl(g\,\Phi_e({\bf u})+(\sigma z_{\bf q}^L)
    {\bf q}\cdot\frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    \calE_{\bf q}^{\sigma L}\biggr)
    +2\calE_{\bf q}^{\sigma L}\gamma_{\bf q}^{\sigma L}+P_{\bf q}^{\sigma L},
      \end{split}
 \label{EpsL}
\end{equation}
\begin{equation}
  \begin{split}
    \frac{\partial{\cal E}_{\bf q}^{\sigma S}}{\partial \tau}
  &=\mu_{\bf q}^S\,\frac{\pi}{q^2}
    \int d{\bf u}\;
    \delta(\sigma z_{\bf q}^S-{\bf q}\cdot{\bf u})
    \biggl[g[\Phi_e({\bf u})+\Phi_i({\bf u})]\\
    &+\,(\sigma z_{\bf q}^L)\,\biggl({\bf q}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    +\frac{m_e}{m_i}\;{\bf q}\cdot
    \frac{\partial \Phi_i({\bf u})}{\partial{\bf u}}\biggr)
    \,\calE_{\bf q}^{\sigma S}\biggr]
    +2\calE_{\bf q}^{\sigma S}\gamma_{\bf q}^{\sigma S}+P_{\bf q}^{\sigma S},
\end{split}
 \label{EpsS}
\end{equation}
where, $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
the collisional damping rate for $L$ and $S$ waves, respectively
\begin{equation}
  \label{GqL}
  \begin{split}
    \gamma_{\bf q}^{\sigma L}&=
    \frac{2gz_{\bf q}^L}{q^2}\int d{\bf q}'
    \frac{({\bf q}\cdot {\bf q'})^2}{{q'}^4
    |\epsilon({\bf q'},z_{\bf q}^L)|^2}
    \left(1+\frac{T_e}{T_i}
    +\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}\\
  &\times\int d{\bf u}\,{\bf q'}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial {\bf u}}
    \delta(z_{\bf q}^L-{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
\begin{equation}
  \label{GqS}
  \begin{split}
    \gamma_{\bf q}^{\sigma S}
    &=\frac{2gz_{\bf q}^L}{q^2}
    \int\frac{d{\bf q}'}{{q'}^4|\epsilon({\bf q'},z_{\bf q}^S)|^2}
    \left(1+\frac{T_e}{T_i}+\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}
    \left(1+\frac{2T_e}{T_i}\frac{{\bf q}\cdot{\bf q}'}{q^2}\right)\\
  &\times \int d{\bf u}\, {\bf q'}
    \cdot\frac{\partial}{\partial {\bf u}}
    \left(\Phi_e({\bf u})+\frac{m_e}{m_i}
    \Phi_i({\bf u})\right)\delta(z_{\bf q}^S
    -{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
and $P_{\bf q}^{\sigma L}$ and $P_{\bf q}^{\sigma S}$ terms depict the
normalized electrostatic bremsstrahlung equations, given by
\begin{equation}
  \begin{split}
    P_{\bf q}^{\sigma L}
  &= \frac{12e^2}{\pi^3}
    \frac{1}{q^2}\frac{1}{(z_{\bf q}^L)^2}
    \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)^2
    \frac{\omega_{pe}^2}{v_e}
    \int d{\bf q'}\,q'^2|{\bf q-q'}|^2\\
  &\times \left[2\left(1+\frac{T_e}{T_i}\right)+q'^2\right]^{-2}
    \left[2\left(1+\frac{T_e}{T_i}\right) +|{\bf q-q'}|^2\right]^{-2}
    \label{PqL}\\
  &\times \int d{\bf u}\int d{\bf u'}
    \delta \left[ \sigma z_{\bf q}^L-{\bf q\cdot u}
    +{\bf q'}\cdot ({\bf u-u'})\right]
    \sum_a \Phi_a({\bf u})\sum_b \Phi_b({\bf u'}),
 \end{split}
\end{equation}
\begin{equation}
  \begin{split}
  P_{\bf q}^{\sigma S}
  &= \mu_{\bf q}\frac{3e^2T_e}{16\pi^3m_e}
    \biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2
    \frac{32}{q^2}\frac{\omega_{pe}^2}{v_e^3}\int d{\bf q}'\\
  &\times\left[2
    \left(1+\frac{T_e}{T_i}\right)+{q'}^2\right]^{-2}
    \left[2 \left(1+\frac{T_e}{T_i}\right)
    +({\bf q}-{\bf q}')^2\right]^{-2}
    \label{PqS}\\
  &\times\int d{\bf u}\int d{\bf u}'\,
    \delta[\sigma z_{\bf q}^L-{\bf q}'\bm{\cdot}{\bf u}'
    -({\bf q}-{\bf q}') \bm {\cdot}{\bf u}]
    \sum_a\Phi_a({\bf u})\sum_b\Phi_b({\bf u}').
  \end{split}
\end{equation}

@@

The ubiquity of inverse power-law velocity distribution in space plasmas
indicates the action of a fundamental physical process; this process may
be the electrostatic bremsstrahlung. For instance, the possibility of the
formation of suprathermal electron velocity distributions in a mildly
collisional environment, as demonstrated in \cite{Tigik2017a}, has a positive
correlation with the velocity filtration model, which rely on the existence
of a high energy electron population in the transition region, located between
the chromosphere and the solar corona, to explain the temperature inversion
observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,Scudder94,
  Scudder96,DS99,DS03,Teles15}.

As a final remark, we would like to emphasize the fundamental aspect of the
theory presented in Ref. \cite{YZKS16}. The rigorous analysis performed during
this doctoral research, suggest that collisional interactions involving charged
particles enfold physical processes that go beyond the Coulomb collisions
effects. An enthralling prospect of this study lies in the possibility of these
underlying kinetic processes being connected to unexplained phenomena observed
in space plasmas. On that regard...

% It is time for new advances in the kinetic description of plasmas. For
% a long time, space observations could only resolve physical phenomena occurring
% in macroscopic scales, described by the magnetohydrodynamic (MHD) theory.

% A better understanding of the combined action of collective and collisional
% plasma processes has some important impact on how observational data from
% denser regions of the solar corona are analyzed. Now that the Parker solar
% probe 
% The prospects of this research are promising. Besides including the
% new effects on the time evolution of nonlinear beam-plasma interaction,
% we are planning the inclusion of effects due to non-homogeneous
% medium on the beam-plasma dynamics, and its implementation in the numerical
% code. Furthermore, the results regarding
% the electrostatic bremsstrahlung term deserve further research in order
% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
% the electrostatic bremsstrahlung being the underlying effect behind the
% generation of suprathermal velocity distributions, which are pervasively
% observed in space plasmas. The objectives above are in accordance with
% the research project approved for the ``Sandwich Doctorate Program'',
% that is proposed to occur under the supervision of Dr. Peter Yoon in the
% University of Maryland.

% \section{Schedule}
% \label{sec:schedule}
% The expected schedule for the remaining period of this doctoral
% research is detailed below:
% \begin{itemize}
% \item \textbf{March to July 2018:} inclusion the new effects on
%   the time evolution of nonlinear beam-plasma interaction, and of
%   implementation the code for the inclusion of non-homogeneous
%   medium on the beam-plasma dynamics;
% \item \textbf{August 2018 to February 2019:} internship period in
%   the University of Maryland, working on the further development
%   of the electrostatic bremsstrahlung hypothesis;
% \item \textbf{March to August of 2019:} Thesis elaboration.
% \end{itemize}

@@

Since this approximation assumes the dominant frequency range on the
denominators is given by the dispersion relation of Langmuir waves
(see Eq. \eqref{dom-freq}), which are high frequency oscillations
near the electron plasma frequency, it is not suitable for use on
the bremsstrahlung expression for $S$ waves.

@@

\chapter{Applications to astrophysical plasmas}
\label{appD}
Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
in the outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks,
and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of the
observable matter in the universe is in the plasma state. Under cosmic conditions,
even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
the atmosphere of cold stars have a strong reaction to electromagnetic fields,
exhibiting the characteristic collective behavior of plasmas and, therefore, are
also considered plasmas\cite{tsypa,may,peratt2014}.

>>>>

In terms of the normalized variables and quantities, the equations
for $L$ and $S$ waves, including the contributions from non-eigenmode
fluctuations, become
\begin{equation}
  \begin{split}
    \frac{\partial\calE_{\bf q}^{\sigma L}}{\partial\tau}
  &=\mu_{\bf q}^L\,\frac{\pi}{q^2}\int d{\bf u}\;
    \delta(\sigma z_{\bf q}^L-{\bf q}\cdot{\bf u})\\
    &\times\biggl(g\,\Phi_e({\bf u})+(\sigma z_{\bf q}^L)
    {\bf q}\cdot\frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    \calE_{\bf q}^{\sigma L}\biggr)
    +2\calE_{\bf q}^{\sigma L}\gamma_{\bf q}^{\sigma L}+P_{\bf q}^{\sigma L},
      \end{split}
 \label{EpsL}
\end{equation}
\begin{equation}
  \begin{split}
    \frac{\partial{\cal E}_{\bf q}^{\sigma S}}{\partial \tau}
  &=\mu_{\bf q}^S\,\frac{\pi}{q^2}
    \int d{\bf u}\;
    \delta(\sigma z_{\bf q}^S-{\bf q}\cdot{\bf u})
    \biggl[g[\Phi_e({\bf u})+\Phi_i({\bf u})]\\
    &+\,(\sigma z_{\bf q}^L)\,\biggl({\bf q}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    +\frac{m_e}{m_i}\;{\bf q}\cdot
    \frac{\partial \Phi_i({\bf u})}{\partial{\bf u}}\biggr)
    \,\calE_{\bf q}^{\sigma S}\biggr]
    +2\calE_{\bf q}^{\sigma S}\gamma_{\bf q}^{\sigma S}+P_{\bf q}^{\sigma S},
\end{split}
 \label{EpsS}
\end{equation}
where $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
the collisional damping rate for $L$ and $S$ waves, respectively
\begin{equation}
  \label{GqL}
  \begin{split}
    \gamma_{\bf q}^{\sigma L}&=
    \frac{2gz_{\bf q}^L}{q^2}\int d{\bf q}'
    \frac{({\bf q}\cdot {\bf q'})^2}{{q'}^4
    |\epsilon({\bf q'},z_{\bf q}^L)|^2}
    \left(1+\frac{T_e}{T_i}
    +\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}\\
  &\times\int d{\bf u}\,{\bf q'}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial {\bf u}}
    \delta(z_{\bf q}^L-{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
\begin{equation}
  \label{GqS}
  \begin{split}
    \gamma_{\bf q}^{\sigma S}
    &=\frac{2gz_{\bf q}^L}{q^2}
    \int\frac{d{\bf q}'}{{q'}^4|\epsilon({\bf q'},z_{\bf q}^S)|^2}
    \left(1+\frac{T_e}{T_i}+\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}
    \left(1+\frac{2T_e}{T_i}\frac{{\bf q}\cdot{\bf q}'}{q^2}\right)\\
  &\times \int d{\bf u}\, {\bf q'}
    \cdot\frac{\partial}{\partial {\bf u}}
    \left(\Phi_e({\bf u})+\frac{m_e}{m_i}
    \Phi_i({\bf u})\right)\delta(z_{\bf q}^S
    -{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
and $P_{\bf q}^{\sigma L}$ and $P_{\bf q}^{\sigma S}$ terms depict the
normalized electrostatic bremsstrahlung equations, given by
\begin{equation}
  \begin{split}
    P_{\bf q}^{\sigma L}
  &= \frac{12e^2}{\pi^3}
    \frac{1}{q^2}\frac{1}{(z_{\bf q}^L)^2}
    \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)^2
    \frac{\omega_{pe}^2}{v_e}
    \int d{\bf q'}\,q'^2|{\bf q-q'}|^2\\
  &\times \left[2\left(1+\frac{T_e}{T_i}\right)+q'^2\right]^{-2}
    \left[2\left(1+\frac{T_e}{T_i}\right) +|{\bf q-q'}|^2\right]^{-2}
    \label{PqL}\\
  &\times \int d{\bf u}\int d{\bf u'}
    \delta \left[ \sigma z_{\bf q}^L-{\bf q\cdot u}
    +{\bf q'}\cdot ({\bf u-u'})\right]
    \sum_a \Phi_a({\bf u})\sum_b \Phi_b({\bf u'}),
 \end{split}
\end{equation}
\begin{equation}
  \begin{split}
  P_{\bf q}^{\sigma S}
  &= \mu_{\bf q}\frac{3e^2T_e}{16\pi^3m_e}
    \biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2
    \frac{32}{q^2}\frac{\omega_{pe}^2}{v_e^3}\int d{\bf q}'\\
  &\times\left[2
    \left(1+\frac{T_e}{T_i}\right)+{q'}^2\right]^{-2}
    \left[2 \left(1+\frac{T_e}{T_i}\right)
    +({\bf q}-{\bf q}')^2\right]^{-2}
    \label{PqS}\\
  &\times\int d{\bf u}\int d{\bf u}'\,
    \delta[\sigma z_{\bf q}^L-{\bf q}'\bm{\cdot}{\bf u}'
    -({\bf q}-{\bf q}') \bm {\cdot}{\bf u}]
    \sum_a\Phi_a({\bf u})\sum_b\Phi_b({\bf u}').
  \end{split}
\end{equation}

@@

The ubiquity of inverse power-law velocity distribution in space plasmas
indicates the action of a fundamental physical process that might -or
might not- be the electrostatic bremsstrahlung. For instance, the possibility
of the formation of suprathermal electron velocity distributions in a mildly
collisional environment, as demonstrated in \cite{Tigik2017a}, has a positive
correlation with the velocity filtration model, which relies on the existence
of a high energy electron population in the solar transition region, located
between the chromosphere and the solar corona, to explain the temperature
inversion observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,
  Scudder94,Scudder96,DS99,DS03,Teles15}.

% As a final remark, i
It is important to emphasize the fundamental aspect of the
theory presented in Ref. \cite{YZKS16}. The rigorous analysis performed during
this doctoral research, suggests that collisional interactions involving charged
particles enfold physical processes that go beyond the Coulomb collisions
effects. An enthralling prospect of this study lies in the possibility of these
underlying kinetic processes being connected to unexplained phenomena observed
in space plasmas. On that regard, the electrostatic weak turbulence theory for
collisional plasmas is a first step towards a more accurate description of the
microscopic physics of plasmas. Further development should extend this formalism
to include electromagnetic waves and, in the long term, the influence of ambient
magnetic field.

These efforts on improving the theoretical description of kinetic processes in
plasmas and numerically analyzing the equations are just in time with current
technological progress in the resolution capability of spacecraft measurement
equipment. A great example of this new trend is the Magneto-spheric Multiscale
(MMS) mission that investigates the physics of magnetic reconnection in the
Earth's magnetosphere. Equipped with high-precision instruments \cite{Pollock2016,
  Torbert2016}, MMS was capable of directly measure wave-particle energy
exchange process in the ion kinetic scale \cite{Gershman2017}, for the first
time. Therefore, it is becoming evident that the kinetic scale is the next
frontier in observational plasma physics, and this will require a more accurate
and comprehensive theory.

@@

Since this approximation assumes that the dominant frequency range on
the denominators is given by the dispersion relation of Langmuir waves
(see Eq. \eqref{dom-freq}), which are high frequency oscillations
near the electron plasma frequency, it is not suitable for use on
the bremsstrahlung expression for $S$ waves.

@@

\chapter{Applications to astrophysical plasmas}
\label{appD}
Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
in the outer layers of Earth's atmosphere, passing through the solar wind in the
interplanetary space, to the stellar interiors and atmospheres, accretion disks
and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
observable matter in the universe is in the plasma state. Under cosmic conditions,
even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
the atmosphere of cold stars have a strong reaction to electromagnetic fields,
exhibiting the characteristic collective behavior of plasmas and, therefore, are
also considered plasmas\cite{tsypa,may,peratt2014}.
